Global Reach or Out of Reach

### 2019-05-10 Paper_markdown.Rmd
Working

---
title: "Paper_text_working_file"
author: "Addison"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Packages

install.packages("tidyverse")
install.packages("DataCombine")
install.packages("dotwhisker")
install.packages("data.table")
install.packages("mlogit")
install.packages("margins")
install.packages("nnet")
install.packages("reshape2")

@@

#Data generation process 
#Prepping datasets for merging.

@@

Master <- politically_relevant %>%
  rename(
    ccodea = ccode1,
    ccodeb = ccode2, 
  ) 
view(Master)

#Merging datasets

@@

Master2 <- inner_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

#Merging in polity iv datasets a and b.
Master2 <- inner_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
Master2 <- inner_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
summary(Master2)

#merging in data on US naval capabilities
Master2 <- inner_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))

@@

#merging in data on material capabilities
Master2 <- inner_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
Master2 <- inner_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year < 2012, year >= 1950)
summary(Master3)

#Variable Generation

@@

#Creating variable measuring relative capabilities
Master3 <- filter(Master3, cinca != -9, cincb != -9)
Master3 <- Master3 %>%
    mutate(Relative_Cap = cinca/(cinca+cincb))
head(Master3$Relative_Cap, 1000)

@@

Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid)
summary(Master4)

Master5 <- full_join(Master4, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

Master5 <- Master5 %>%
    mutate(Ally =0)
Master5$Ally[Master5$neutrality==1] <- 1 
Master5$Ally[Master5$nonaggression==1] <- 1 
Master5$Ally[Master5$defense==1] <- 1 
Master5$Ally[Master5$entente==1] <- 1

#Statistical Tests

@@

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
dwplot(MID_Full_Log)

@@

>>>>

---
title: "Global Reach or Out of Reach"
author: "Addison Huygens"
date: "May 10, 2019"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: no
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
  word_document: default
citecolor: black
biblio-style: apsr
endnote: no
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("tidyverse")
install.packages("DataCombine")
install.packages("dotwhisker")
install.packages("data.table")
install.packages("mlogit")
install.packages("margins")
install.packages("nnet")
install.packages("reshape2")

@@

```
#Packages

```
#Data generation process 
#Prepping datasets for merging.

@@

Master <- politically_relevant %>%
  rename(
    ccodea = ccode1,
    ccodeb = ccode2, 
  ) 
view(Master)
```

```
#Merging datasets

@@

Master2 <- merge(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), all.x = TRUE, all.y = TRUE)

Master2 <- left_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

#Merging in polity iv datasets a and b.
Master2 <- left_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
Master2 <- left_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
summary(Master2)

#merging in data on US naval capabilities
Master2 <- left_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))

@@

#merging in data on material capabilities
Master2 <- left_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
Master2 <- left_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))

Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year < 2012, year >= 1950)
summary(Master3)
```

```
#Variable Generation

@@

#Creating variable measuring relative capabilities
Master3 <- filter(Master3, cinca != -9, cincb != -9)
Master3 <- Master3 %>%
    mutate(Relative_Cap = cinca/cincb)
head(Master3$Relative_Cap, 1000)

@@

Master4 <- Master3 %>%
    mutate(Ally =0)
Master4$Ally[Master4$neutrality==1] <- 1 
Master4$Ally[Master4$nonaggression==1] <- 1 
Master4$Ally[Master4$defense==1] <- 1 
Master4$Ally[Master4$entente==1] <- 1

Master4 <- select(Master4, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
summary(Master4)
```

```
#Statistical Tests

@@

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally, data = Master4, family=binomial)
summary(MID_Full_Log) 
dwplot(MID_Full_Log)

@@

```

This is a test
